\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Gabriel Esteban Pinochet Soto}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.4cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{20} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.75}

% define space between list items
\newcommand{\listitemspace}{0.175em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {mathematics, numerical analysis, functional analysis},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.32\textwidth}
        %{\bf Nationality:} Chilean.\\
        %{\bf Date of Birth:} September 26, 1997.\\
        {\bf Languages:}\\ Spanish (native), \\English (intermediate), \\ French (basic). 
    \end{minipage}
    \begin{minipage}[t]{0.32\textwidth}
        {\bf Email:}\\
        \href{mailto:gpin2@pdx.edu}{gpin2@pdx.edu}\\
        % \href{mailto:gpinochetsoto@anl.gov}{gpinochetsoto@anl.gov}\\
        \href{mailto:gpinochetsoto@gmail.com}{gpinochetsoto@gmail.com}
    \end{minipage}
    \begin{minipage}[t]{0.32\textwidth}
        {\bf Websites:}\\
        \href{https://web.pdx.edu/~gpin2/}{https://web.pdx.edu/\textasciitilde gpin2/}\\
        \href{https://homeomorfismo.github.io/}{https://homeomorfismo.github.io/}\\
    \end{minipage}
    \hfill

    \section*{Career Objective}

    % Incipient mathematician.
    % Seeking to do research and teach.
    Interested in numerical methods and applied mathematics, specifically on the theoretical fundament of these.
    Principal interests are Linear Functional Analysis, Partial Differential Equations, and Finite Element Methods.
    Currently working as a Graduate Research Assistant at PSU.
    Currently interest are adaptivity algorithms for FEM, saddle-point solvers, and applications. 

    \subsection*{Skills}

    Critical thinking and mathematical reasoning.\\
    Familiarized with C/C++, MATLAB, Python, NGSolve, Git.\\
    Self-motivated student, enthusiastic, team-worker.
    % Empathic, dedicated, creative.

    % \section*{Interest Research Areas}

    % Analysis and implementation of the Finite Element Method. Developing numerical methods for differential equations. 
    
    \section*{Education}

    \begin{tablist}
        \item[Ph.D.] \tab Mathematical Sciences, Portland State University. September 2021--Today. \emph{In progress}.
        \item[M.S.]  \tab Pure Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso, March 2021--December 2021.
        \item[B.S.]  \tab Pure Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso, March 2016--December 2019.
        \item[H.S.] \tab Colegio Rub\'en Castro, March 2012--December 2015. \emph{(High School equivalent)}.

    \end{tablist}

    \subsection*{Complementary education and minicourse attendance}

    \begin{tablist}

	\item[2022] \tab \emph{3rd Biennial Metting of SIAM Pacific Nothwest Section.} Washington State University Vancouver, Vancouver, WA. May 20--May 22.

        \item[2019] \tab \emph{French Latin-American Conference on New Trends in Applied Mathematics.} Center for Mathematical Modeling, Universidad de Chile. Nov 5--Nov 8.

        \item[2019] \tab \emph{Functional Analysis,} taught by Claudio Landim. Instituto Nacional de Matem\'atica Pura e Aplicada. Jan 7--Mar 1.
        
        \item[2018] \tab \emph{Second NGSolve User Meeting,} orginized by Joachim Schöberl, Christoph Lehrenfeld
        Christopher Lackner, and Christoph Wintersteiger. Göttingen. Jul 4--Jul 6. 

        \item[2018] \tab \emph{Introduction to elliptical functions,} taught by Victor Moll. Pontificia Universidad Cat\'olica de Valpara\'iso. Jul 24--Aug 24.
        
        \item[2017] \tab \emph{Fast and smooth simulation of space-time problems,} taught by Maciej Paszynski. Pontificia Universidad Cat\'olica de Valpara\'iso. Jul 24--Jul 28.
        
        \item[2017] \tab \emph{Coding the FEM II,} taught by David Pardo and \'Angel Rodr\'iguez-Rozas. Pontificia Universidad Cat\'olica de Valpara\'iso. Jan 15--Jan 20. 

        \item[2016]  \tab \emph{Training program for teaching assistants}. Pontificia Universidad Cat\'olica de Valpara\'iso.\\ Sep 26--Oct 31.
        
        \item[2013--15] \tab \emph{Educational Program for Academic Talents BETA}. Pontificia Universidad Cat\'olica de Valpara\'iso.

    \end{tablist}

    \section*{Publications}

    \begin{tablist}

    \item[2021] \tab Aralar Erdozain, Ignacio Muga, Victor P\'eron, Gabriel Pinochet. Semi-analytical solutions for the problem of the electric potential set in a borehole with a highly conductive casing. \href{https://hal.archives-ouvertes.fr/hal-03373028}{Preprint ⟨hal-03373028⟩.} \href{https://link.springer.com/article/10.1007/s13137-022-00197-3}{ Published in International Journal on Geomathematics.}

    \end{tablist}

    \section*{Achievements}

    \begin{tablist}

        \item[2021] \tab Dean's Oregon Sports Lottery Graduate Scholarship, Portland State University, Fall Term. 10,000 USD, for academic year of 2021-2022.

        \item[2021] \tab Departmental Scholarship, Portland State University, Fall Term - Spring Term. 2,000 USD per term, for the academic year of 2021-2022.

        % \item[2017] \tab Best academic performance for newcomers in 2016, Pontificia Universidad Cat\'olica de Valpara\'iso.

        \item[2016] \tab Pontificia Universidad Cat\'olica de Valpara\'iso Scholarship, Pontificia Universidad Cat\'olica de Valpara\'iso. Four-year full tuition remission scholarship awarded for academic excellence in high school and good performance on the national University Selection Test (Prueba de Selecci\'on Universitaria).

    \end{tablist}

    \section*{Talks}

    \begin{tablist}

	\item[2022] \tab \emph{NGS-PETSc Interface.} CADES RTG Group Meeting, Portland State University, Portland, OR, US. November 28.

	\item[2022] \tab \emph{Semi-Analytical Solutions for Asymptotic Models for the Electric Potential across a Highly Conductive Casing.} Applied \& Computational Math Seminar, Portland State University, Portland, OR, US. Apr 4.

        \item[2020] \tab \emph{Conservative Numerical Methods for the resolutions of ODEs.} Coloquio de Licenciatura, Instituto de Matem\'aticas, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. Sep 3.
         
        \item[2020] \tab \emph{Conservative Numerical Methods for the resolutions of ODEs.} Seminario de Estudiantes, Universidad de Chile. Santiago, Chile. May 29.

    	\item[2019] \tab \emph{Different numerical methods for the resolution of positive ODEs with linear invariants.} Generaci\'on de Conocimiento, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. Oct 10.
    
    	\item[2019] \tab \emph{Introduction to Theory of Computation.} Coloquio de Licenciatura, Instituto de Matem\'aticas, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. May 23.
    	
    \end{tablist}


    \section*{Relevant Professional Experience}

	\begin{tablist}

        \item[2022--2022] \emph{Intern}. Under the supervision of \href{https://people.llnl.gov/lee1029}{Dr.~Chak Shing Lee}. Computing Scholar Program, Lawrence Livermore National Laboratory. June 2023--September 2023.

        \item[2022--2023] \emph{Graduate Research Assistant}. Under the supervision of \href{https://web.pdx.edu/~gjay/}{Dr.~Jay Gopalakrishnan}. Portland State University. September 2022--June 2023.

        \item[2022--2022] \emph{Givens Associate}. Under the supervision of \href{https://climatemodeling.org/~rmills/}{Dr.~Richard Tran Mills}. MCS Mathematics \& Computer Science Division, Argonne National Laboratory. July 2022--September 2022.

	\end{tablist}


    \subsection*{Graduate Teaching Assistant}

    \begin{tablist}

        \item[2022] \tab \emph{Introduction to Linear Algebra}. Portland State University. April 2022--June 2022.

        \item[2022] \tab \emph{Introduction to College Mathematics II}. Portland State University. January 2022--March 2022.

        \item[2021] \tab \emph{Introduction to College Mathematics II}. Portland State University. September 2021--December 2021. 
    
    \end{tablist}

    \subsection*{Teaching Assistant}

    \begin{tablist}

        \item[2020] \tab \emph{Functional Analysis}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. July 2020--December 2020.
            
        \item[2020] \tab \emph{Multivariable Calculus}. Civil Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. July 2020--December 2020.
            
        \item[2020] \tab \emph{Integral Calculus}. Mechanical Engineering, Mining Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. July 2020--December 2020.
            
        \item[2020] \tab \emph{Linear Algebra 2}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2020--June 2020.
            
        \item[2020] \tab \emph{Multivariable Calculus}. Physics, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2020--June 2020.
            
        \item[2020] \tab \emph{Multivariable Calculus}. Industrial chemistry, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2020--June 2020.
        
        \item[2019] \tab \emph{General Topology}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2019--December 2019.
            
        \item[2019] \tab \emph{Measure theory}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2019--December 2019.
            
        \item[2018] \tab \emph{C Programming}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. July 2018--December 2018.
            
        \item[2018] \tab \emph{Multivariable Calculus}. Chemical Engineering, Biochemical Engineering, Engineering in extractive metallurgy, Pontificia Universidad Cat\'olica de Valpara\'iso. January 2018--June 2018.
         
        \item[2017] \tab \emph{Riddles and Number Series: Discovering the mathematics of everyday life}. Educational Program for Academic Talents BETA, Pontificia Universidad Cat\'olica de Valpara\'iso.

        \item[2017] \tab \emph{C Programming}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. July 2017--December 2017.
            
        \item[2017] \tab \emph{Differential Calculus}. Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. March 2017--June 2017.

    \end{tablist}
    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
