

\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{Gabriel Esteban Pinochet Soto}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{helvet}     % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.4cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{20} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.75}

% define space between list items
\newcommand{\listitemspace}{0.175em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {mathematics, numerical analysis, functional analysis},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.55\textwidth}
        %{\bf Nationality:} Chilean.\\
        %{\bf Date of Birth:} September 26, 1997.\\
        {\bf Languages:}\\ Spanish (native), \\English (intermediate), French (basic). \\
    \end{minipage}
    %\begin{minipage}[t]{0.4\textwidth}
        %{\bf Email:}\\
        %\href{mailto:gpin2@pdx.edu}{gpin2@pdx.edu}\\
        %\href{mailto:gpinochetsoto@gmail.com}{gpinochetsoto@gmail.com}\\
        %{\bf Mobile number:} 971 380 6881
    %\end{minipage}
    \hfill

    \section*{Career Objective}

    % Incipient mathematician.
    % Seeking to do research and teach.
    Interested in numerical methods and applied mathematics, specifically on the theoretical fundament of these.
    Principal interests are Linear Functional Analysis, Partial Differential Equations, and Finite Element Methods.
    % Currently working as a Graduate Teaching Assistant at PSU.
    Currently interest are axisymmetric settings for FEM.

    \subsection*{Skills}

    Critical thinking and mathematical reasoning.\\
    Familiarized with C, MATLAB, Python, NGSolve, Git.\\
    Self-motivated student, enthusiastic, team worker.
    % Empathic, dedicated, creative.

    % \section*{Interest Research Areas}

    % Analysis and implementation of the Finite Element Method. Developing numerical methods for differential equations. 
    
    \section*{Education}

    \begin{tablist}
        \item[M.S.]  \tab Pure Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso, 2021.
        \item[B.S.]  \tab Pure Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso, 2019.
        %\item[Ph.D.] \tab Mathematical Sciences, Portland State University, 2021.
    \end{tablist}

    \subsection*{Currently Studying}

    \begin{tablist}
        
        \item[Ph.D.] \tab Mathematical Sciences, Portland State University. Started in September 2021.
        %\item[M.S.]  \tab Pure Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. Started in March 2021.
    \end{tablist}

    \subsection*{Complementary education and minicourse attendance}

    \begin{tablist}

        \item[2019] \tab \emph{French Latin-American Conference on New Trends in Applied Mathematics.} Center for Mathematical Modeling, Universidad de Chile. Nov 5--Nov 8.

        \item[2019] \tab \emph{Functional Analysis,} taught by Claudio Landim. Instituto Nacional de Matem\'atica Pura e Aplicada. Jan 7--Mar 1.
        
        \item[2018] \tab \emph{Second NGSolve User Meeting,} orginized by Joachim Schöberl, Christoph Lehrenfeld
        Christopher Lackner, and Christoph Wintersteiger. Göttingen. Jul 4--Jul 6. 

        % \item[2018] \tab \emph{Introduction to elliptical functions,} taught by Victor Moll. Pontificia Universidad Cat\'olica de Valpara\'iso. Jul 24--Aug 24.
        
        \item[2017] \tab \emph{Fast and smooth simulation of space-time problems,} taught by Maciej Paszynski. Pontificia Universidad Cat\'olica de Valpara\'iso. Jul 24--Jul 28.
        
        \item[2017] \tab \emph{Coding the FEM II,} taught by David Pardo and \'Angel Rodr\'iguez-Rozas. Pontificia Universidad Cat\'olica de Valpara\'iso. Jan 15--Jan 20. 

        % \item[2016]  \tab \emph{Training program for teaching assistants}. Pontificia Universidad Cat\'olica de Valpara\'iso.\\ Sep 26--Oct 31.
        
        % \item[2013--15] \tab \emph{Educational Program for Academic Talents BETA}. Pontificia Universidad Cat\'olica de Valpara\'iso.

    \end{tablist}

    \section*{Publications}

    \begin{tablist}

    \item[2021] \tab Aralar Erdozain, Ignacio Muga, Victor P\'eron, Gabriel Pinochet. Semi-analytical solutions for the problem of the electric potential set in a borehole with a highly conductive casing. \href{https://hal.archives-ouvertes.fr/hal-03373028}{⟨hal-03373028⟩}. \emph{Preprint. Submitted to International Journal on Geomathematics.}

    \end{tablist}

    \section*{Achievements}

    \begin{tablist}

        \item[2021] \tab Dean's Oregon Sports Lottery Graduate Scholarship, Portland State University, Fall Term. 10,000 USD, for academic year of 2021-2022.

        \item[2021] \tab Departmental Scholarship, Portland State University, Fall Term - Spring Term. 2,000 USD per term, for the academic year of 2021-2022.

        % \item[2017] \tab Best academic performance for newcomers in 2016, Pontificia Universidad Cat\'olica de Valpara\'iso.

        \item[2016] \tab Pontificia Universidad Cat\'olica de Valpara\'iso Scholarship, Pontificia Universidad Cat\'olica de Valpara\'iso. Four-year full tuition remission scholarship awarded for academic excellence in high school and good performance on the national University Selection Test (Prueba de Selecci\'on Universitaria).

    \end{tablist}

    \section*{Talks}

    \begin{tablist}

	\item[2022] \tab \emph{Semi-Analytical Solutions for Asymptotic Models for the Electric Potential across a Highly Conductive Casing.} Applied & Computational Math Seminar, Portland State University, Portland, OR, US. Apr 4.

        \item[2020] \tab \emph{Conservative Numerical Methods for the resolutions of ODEs.} Coloquio de Licenciatura, Instituto de Matem\'aticas, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. Sep 3.
         
        \item[2020] \tab \emph{Conservative Numerical Methods for the resolutions of ODEs.} Seminario de Estudiantes, Universidad de Chile. Santiago, Chile. May 29.

    	\item[2019] \tab \emph{Different numerical methods for the resolution of positive ODEs with linear invariants.} Generaci\'on de Conocimiento, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. Oct 10.
    
    	\item[2019] \tab \emph{Introduction to Theory of Computation.} Coloquio de Licenciatura, Instituto de Matem\'aticas, Pontificia Universidad Cat\'olica de Valpara\'iso. Valpara\'iso, Chile. May 23.
    	
    \end{tablist}



    \section*{Teaching Experience}

    \subsection*{Graduate Teaching Assistant}

    \begin{tablist}

        \item[2022] \tab \emph{Introduction to Linear Algebra}. Portland State University. Spring Term.

        \item[2022] \tab \emph{Introduction to College Mathematics II}. Portland State University. Winter Term.

        \item[2021] \tab \emph{Introduction to College Mathematics II}. Portland State University. Fall Term. 
    
    \end{tablist}

    \subsection*{Teaching Assistant}

    \begin{tablist}

        \item[2020] \tab \emph{Functional Analysis}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2020] \tab \emph{Multivariable Calculus}. Civil Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2020] \tab \emph{Integral Calculus}. Mechanical Engineering, Mining Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2020] \tab \emph{Linear Algebra 2}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso.
            
        \item[2020] \tab \emph{Multivariable Calculus}. Physics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2020] \tab \emph{Multivariable Calculus}. Industrial chemistry, Pontificia Universidad Cat\'olica de Valpara\'iso. 
        
        \item[2019] \tab \emph{General Topology}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2019] \tab \emph{Measure theory}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2018] \tab \emph{C Programming}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2018] \tab \emph{Multivariable Calculus}. Chemical Engineering, Biochemical Engineering, Engineering in extractive metallurgy, Pontificia Universidad Cat\'olica de Valpara\'iso. 
         
        % \item[2017] \tab \emph{Riddles and Number Series: Discovering the mathematics of everyday life}. Educational Program for Academic Talents BETA, Pontificia Universidad Cat\'olica de Valpara\'iso.

        \item[2017] \tab \emph{C Programming}. Mathematics, Pontificia Universidad Cat\'olica de Valpara\'iso. 
            
        \item[2017] \tab \emph{Differential Calculus}. Engineering, Pontificia Universidad Cat\'olica de Valpara\'iso. 

    \end{tablist}
    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
